\documentclass[11pt,letterpaper]{article}

% ---------------------------
% Packages (keep it sober)
% ---------------------------
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} % robust on Overleaf pdfLaTeX
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}

% Additions for framed responses
\usepackage{xcolor}
\usepackage{mdframed}

% ---------------------------
% Unicode safety (prevents "missing later text" due to smart quotes/dashes)
% ---------------------------
\DeclareUnicodeCharacter{201C}{``}
\DeclareUnicodeCharacter{201D}{''}
\DeclareUnicodeCharacter{2019}{'}
\DeclareUnicodeCharacter{2013}{--}
\DeclareUnicodeCharacter{2014}{---}
\DeclareUnicodeCharacter{2026}{\ldots}
\DeclareUnicodeCharacter{2022}{$\bullet$}
% Robust handling of NBSP (U+00A0) without relying on pasting an invisible char
\DeclareUnicodeCharacter{00A0}{~}

% ---------------------------
% Spacing / lists
% ---------------------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\setlist[itemize]{leftmargin=1.4em, itemsep=3pt, topsep=3pt}
\setlist[enumerate]{leftmargin=1.6em, itemsep=3pt, topsep=3pt}

% ---------------------------
% Section styling (simple)
% ---------------------------
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{}{}{ }
\titlespacing{\section}{0pt}{10pt}{6pt}
\titlespacing{\subsection}{0pt}{8pt}{4pt}

% ---------------------------
% Minimal environments
% ---------------------------
\newcommand{\commentheading}[1]{%
  \vspace{6pt}\noindent\textbf{Comment (#1)}\par
  \vspace{2pt}\hrule\vspace{6pt}
}
\newenvironment{commentblock}{\begin{quote}\small\itshape}{\end{quote}}
\newcommand{\responseheading}{%
  \vspace{2pt}\noindent\textbf{Response}\par
}
% ---------------------------
% Framed response boxes
% ---------------------------
\mdfdefinestyle{plainbox}{
  linewidth=0.4pt,
  linecolor=black!35,
  backgroundcolor=white,
  roundcorner=0pt,
  innertopmargin=6pt,
  innerbottommargin=6pt,
  innerleftmargin=6pt,
  innerrightmargin=6pt,
  skipabove=6pt,
  skipbelow=6pt
}
\newenvironment{responsebox}{\begin{mdframed}[style=plainbox]}{\end{mdframed}}

% ---------------------------
% ID macros
% ---------------------------
\newcommand{\HE}[1]{HE-#1}
\newcommand{\RoneO}{R1-O}
\newcommand{\RoneM}[1]{R1-M#1}
\newcommand{\Ronem}[1]{R1-m#1}

% ---------------------------
% Title
% ---------------------------
\title{\textbf{Response to the Editor and Reviewer 1}\\
Manuscript ID: 5228655 (\emph{Environmetrics})}
\author{Antonio Aguirre \and Raquel Prado \and Bruno Sans\'o}
\date{Prepared April 2026}

% =========================
% INTERNAL TODOs 
% Remove this block before submission.
% =========================
% TODO[HE-2][HOLD]: Justify why only five cutoffs were retained after enforcing
% archive feasibility and version consistency. Pending Raquel's input.
% TODO[HE-3][OPTIONAL]: Insert an exact manuscript section number later if we
% decide that the generic forecasting-results reference should be made explicit.
% TODO[HE-4][OPTIONAL]: Insert an exact manuscript section number later if we
% decide that the generic forecasting-validation reference should be explicit.
% TODO[HE-6][OPEN]: Mirror the forecast-input timing clarification explicitly in
% the revised manuscript when the forecasting-design subsection is rewritten.
% TODO[HE-6][OPEN]: Consider moving the forecast-input availability explanation
% earlier, when the cutoff design is first introduced in the manuscript.
% TODO[R1-M1][BRUNO-REVIEW]: Recheck after the introduction rewrite is complete.
% TODO[R1-M2][BRUNO-REVIEW]: Recheck after the final methodology/results
% structure is fixed.
% TODO[R1-M3][BRUNO-REVIEW]: Recheck after the final level of mathematical
% streamlining in the manuscript is decided.
% TODO[R1-m4][BRUNO-REVIEW]: Recheck after the final data/application section
% structure is fixed in the manuscript.
% TODO[R1-m7][BRUNO-REVIEW]: Recheck after the final results-section headings and
% subsection structure are fixed.
% TODO[R1-m9][BRUNO-REVIEW]: Recheck after the final decision on Figures 8 and 9
% in the manuscript.

\begin{document}
\maketitle
\begin{flushleft}
Dear Professor Fass\`o,
\end{flushleft}

We thank you and the reviewer for the careful reading of our manuscript and for the constructive suggestions. We found the comments very helpful and have revised the paper substantially in response.

The revision described below strengthens the forecasting evaluation and clarifies the manuscript structure. In particular, we rebuilt the forecasting analysis around five version-consistent rolling-origin cutoffs, added direct comparisons against simpler Bayesian alternatives and the raw ECMWF/GloFAS and NWS forecast products, added forecast-window CRPS and targeted quantile diagnostics, and included a targeted ablation study of the strongest model specification. We also revised the manuscript to clarify the roles of the different data sources, streamline parts of the methodological exposition, and make the computational and reproducibility discussion more explicit.

Detailed point-by-point responses follow below.

\section*{Summary of Major Revisions}
\begin{itemize}
\item[] Rebuilt the forecasting validation around five version-consistent rolling-origin cutoffs and compared the proposed method against simpler Bayesian alternatives and the raw ECMWF/GloFAS and NWS forecast products.
\item[] Added forecast-window CRPS and targeted quantile diagnostics, and aligned the final forecasting protocol with the most recent forecast issuance available at each cutoff.
\item[] Added a targeted ablation study of the strongest specification and clarified the forecasting contribution of the Bayesian quantile-based correction-and-synthesis framework.
\item[] Planned manuscript revisions clarify the roles of observations, retrospective products, and forecast products, tighten the methodological exposition, and expand the computational and reproducibility discussion.
\end{itemize}

\newpage

\section{Response to the Handling Editor}

\begin{commentblock}
Handling editor comment:

This paper develops a Bayesian dynamical model approach for river flow forecasting. A reviewer and I have read the manuscript, and although this is an important problem, and the proposed methods are interesting, there are some serious shortcomings of the submitted manuscript that need to be addressed.
\end{commentblock}


\commentheading{\HE{1}}
\begin{commentblock}
- The abstract purports a fast approach to the proposed DQLM framework, but that doesn't seem to be verified anywhere in the manuscript -- what is the computational time and complexity of the proposed method? Once it is fitted, does it need to be reestimated in future months or years? Is it feasible to do so?
\end{commentblock}

\responseheading
\begin{responsebox}
Thank you for pointing this out. The revised manuscript now makes the computational cost and operational feasibility of the forecasting workflow explicit in the abstract and in the forecasting methods/results discussion. For the main model at a single river site, one issuance cycle requires about two hours end-to-end on our production Linux server, with about 100 minutes for fitting and about 20 minutes for post-processing on a 64-core machine with roughly 503 GiB RAM; the seven quantile fits are run in parallel. The model requires refitting as new observations, retrospective products, and forecast inputs become available, and this daily refitting is operationally feasible once the data pipeline is in place. The dominant computational bottleneck is repeated Kalman filtering and smoothing, with leading-order cost proportional to \((T+H)d^{3}\) per full pass, where \(T\) is the historical length, \(H\) the forecast horizon, and \(d\) the latent-state dimension.
\end{responsebox}

%
\commentheading{\HE{2}}
\begin{commentblock}
- One of the main issues with the paper is that the proposed method is not validated properly -- there are no competing alternatives (despite models, A, B and C being listed), the extended asymmetric Laplace is not really given validation either (how does this compare against just an asymmetric Laplace in this problem setting?). I imagine this hierarchical model is likely so complicated that no working hydrologists would understand, nor use it, without very clear evidence that it was substantially superior to other forecast products. The method should be validated against competing statistical models, as well as physical forecast ensembles to illustrate that the predictive distributions are sharper and better calibrated than simpler alternatives.
\end{commentblock}

\responseheading
\begin{responsebox}
We agree that the original manuscript did not validate the proposed forecasting framework strongly enough. In the revised manuscript, we address that directly through a five-cutoff rolling-origin out-of-sample evaluation. At each cutoff, we generate predictive distributions for up to 29 days ahead and verify them against future USGS observations that were not used in model fitting. The revised comparison includes both simpler Bayesian alternatives and the raw ECMWF/GloFAS and NWS forecast products.

Constructing this validation required recovering and harmonizing historical deterministic forecast archives, retrospective products, and forecast covariates across institutions. In the course of this revision, we also corrected the earlier retrospective-input version mismatch so that the final comparisons use only version-consistent forecasting folds.

To describe the models considered, we use the compact label \(L\)-\(S\)-\(T\). Here \(L\in\{\mathrm{N},\mathrm{AL},\mathrm{exAL}\}\), where N denotes Normal Dynamic Linear Model (NDLM), AL denotes Dynamic Quantile Linear Model (DQLM) with asymmetric Laplace likelihood, and exAL denotes exDQLM with extended asymmetric Laplace likelihood. Next, \(S\in\{\mathrm{U},\mathrm{M}\}\), where U is univariate (no retrospective products or forecast ensembles from climate institutions) and M is multivariate (uses retrospective products and forecast ensembles from ECMWF/GloFAS and NWS). Finally, \(T\in\{\mathrm{T0},\mathrm{T1}\}\), where T0 means no transfer function during the forecast window and T1 means the transfer function remains active during the forecast window, using forecast precipitation and soil-moisture covariates from NOAA/GEFS.

\begin{center}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{>{\ttfamily}l >{\raggedright\arraybackslash}p{11cm}}
\toprule
Label & Specification (ordered from simplest to most complex) \\
\midrule
N-U-T1 & Univariate NDLM with transfer function active during the forecast window \\
N-M-T0 & Multivariate NDLM without transfer function during the forecast window \\
N-M-T1 & Multivariate NDLM with transfer function active during the forecast window \\
AL-U-T1 & Univariate DQLM (AL likelihood) with transfer function active during the forecast window \\
AL-M-T0 & Multivariate DQLM (AL likelihood) without transfer function during the forecast window \\
AL-M-T1 & Multivariate DQLM (AL likelihood) with transfer function active during the forecast window \\
exAL-U-T1 & Univariate exDQLM (exAL likelihood) with transfer function active during the forecast window \\
exAL-M-T0 & Multivariate exDQLM (exAL likelihood) without transfer function during the forecast window \\
exAL-M-T1 & Multivariate exDQLM (exAL likelihood) with transfer function active during the forecast window \\
\bottomrule
\end{tabular}
\end{center}

In addition, we benchmark these Bayesian models against the raw ECMWF/GloFAS and NWS forecast products.

All Bayesian models and the two raw forecast products are evaluated on the same transformed discharge scale and under the same preprocessing rules. We use mean forecast-window CRPS as the principal cross-model validation metric and report quantile diagnostics separately.

\medskip
\noindent The table reports mean forecast-window CRPS by cutoff for the nine Bayesian model families and the two raw forecast products. Lower values are better, and the smallest value in each cutoff column is shown in bold.\par
\medskip

\begin{center}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{>{\ttfamily}l rrrrr}
\toprule
Model label & 01/23/2021 & 11/12/2021 & 12/21/2021 & 05/11/2022 & 12/25/2022 \\
\midrule
\multicolumn{6}{l}{\textit{Raw forecast products}} \\
RAW-GLOFAS & 0.5379 & 1.5664 & 1.7757 & 2.0301 & 2.9297 \\
RAW-NWS & 2.6668 & 0.0968 & 1.8160 & 0.7329 & 1.6609 \\
\addlinespace[2pt]
\multicolumn{6}{l}{\textit{Bayesian models (simple to complex)}} \\
N-U-T1 & 0.3520 & 0.2486 & 1.1768 & 0.1572 & 2.1451 \\
N-M-T0 & 0.5311 & 0.0565 & 1.5616 & 0.0241 & 2.3485 \\
N-M-T1 & 0.5275 & 0.0722 & 0.6071 & 0.0416 & 0.5363 \\
AL-U-T1 & 0.2449 & 0.1493 & 1.2283 & 0.0551 & 1.1038 \\
AL-M-T0 & 0.3267 & 2.2435 & 0.6511 & 0.0433 & 2.2601 \\
AL-M-T1 & 0.1604 & 0.0391 & 0.3482 & 0.0214 & 0.6186 \\
exAL-U-T1 & 0.2229 & 0.1506 & 1.2691 & 0.0541 & 1.1189 \\
exAL-M-T0 & 0.3292 & 1.2744 & 0.4720 & 0.0694 & 2.3365 \\
exAL-M-T1 & \textbf{0.1569} & \textbf{0.0284} & \textbf{0.2369} & \textbf{0.0210} & \textbf{0.4375} \\
\bottomrule
\end{tabular}
\end{center}

This comparison addresses the extended asymmetric Laplace question directly. Under the strongest multivariate transfer-function specification, \texttt{exAL-M-T1} has lower forecast-window CRPS than \texttt{AL-M-T1} at all five cutoffs, and it is the best-performing model in all five cutoffs overall. The best corrected model also outperforms the best raw forecast baseline across the panel. These results support the exAL extension empirically, because it gives the strongest forecasting performance among the models and raw forecast products considered.
\end{responsebox}

%
\commentheading{\HE{3}}
\begin{commentblock}
- This brings me to another point, in that the hierarchical model is fairly detailed. A necessary revision would be to implement versions of the model without various hierarchical pieces -- e.g., Model C, what if the AR trend piece were removed? Or, Model B, what if retrospective and/or all states autoregressions were removed? In the current manuscript, the results look decent, but it’s not really clear which part of the model is giving the most “bang for your buck”, which is critical for end users to understand.
\end{commentblock}

\responseheading
\begin{responsebox}
We agree that the original manuscript did not show clearly enough which parts of the hierarchical specification contribute most to forecast skill. In the revised manuscript, we address this with a targeted ablation study of the best-performing model, \texttt{exAL-M-T1}. Each ablation removes one structural component at a time while keeping the cutoff dates, preprocessing, external inputs, and forecasting hyperparameters fixed, so differences in forecast-window CRPS can be attributed to the removed component rather than to a different forecasting setup.

We use the following labels in the ablation study:
\begin{itemize}
\item \texttt{exAL-M-T1} (full reference): trend + three retained seasonal harmonic pairs + transfer-function components, with the transfer function active in both fitting and forecasting;
\item \texttt{exAL-M-T1-noTrend}: the full model without the trend state;
\item \texttt{exAL-M-noTF}: the full model without transfer information in either fitting or the forecast window;
\item \texttt{exAL-M-T1-noH1}, \texttt{exAL-M-T1-noH2}, and \texttt{exAL-M-T1-noH3}: the full model with the first, second, or third retained seasonal harmonic pair removed from the seasonal state block.
\end{itemize}

\medskip
\noindent The table reports mean forecast-window CRPS for the full \texttt{exAL-M-T1} model, its component-wise ablations, and the raw forecast products included as references. Lower values are better, and within the ablation block the smallest value in each cutoff column is shown in bold.\par
\medskip

\begin{center}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{>{\ttfamily}l c c c c c}
\toprule
Ablation model & 01/23/2021 & 11/12/2021 & 12/21/2021 & 05/11/2022 & 12/25/2022 \\
\midrule
exAL-M-T1 (full) & \textbf{0.1569} & \textbf{0.0284} & \textbf{0.2369} & \textbf{0.0210} & \textbf{0.4375} \\
exAL-M-T1-noTrend & 1.1591 & 0.0666 & 1.4134 & 0.2571 & 3.0796 \\
exAL-M-noTF & 0.3421 & 0.0984 & 0.4800 & 0.0383 & 2.3588 \\
exAL-M-T1-noH1 & 0.3536 & 0.1030 & 1.9431 & 0.2777 & 2.0821 \\
exAL-M-T1-noH2 & 0.3932 & 0.1757 & 1.9430 & 0.2795 & 2.0661 \\
exAL-M-T1-noH3 & 0.3552 & 0.1763 & 1.9360 & 0.2226 & 2.3886 \\
\addlinespace[2pt]
\multicolumn{6}{l}{\textit{Raw forecast products (reference only)}} \\
RAW-GLOFAS & 0.5379 & 1.5664 & 1.7757 & 2.0301 & 2.9297 \\
RAW-NWS & 2.6668 & 0.0968 & 1.8160 & 0.7329 & 1.6609 \\
\bottomrule
\end{tabular}
\end{center}

Across all five cutoffs, the full model remains the best ablation configuration. Removing transfer information degrades forecast skill consistently, while the largest losses often come from removing the trend state or one seasonal harmonic pair, especially in the more difficult winter windows. The full \texttt{exAL-M-T1} model also remains better than both raw forecast products at every cutoff. These ablation results indicate that the gain of \texttt{exAL-M-T1} comes from the combined contribution of transfer information, trend, and multi-frequency seasonality. They are now summarized in the revised forecasting-results section of the manuscript.

\end{responsebox}


\commentheading{\HE{4}}
\begin{commentblock}
- Again, on validation: include (along with comparisons against alternative models) proper scores quantifying the quality of the predictive distributions. CRPS is used in model estimation, apparently, but why are CRPS scores not reported out for the forecasting exercise? And, how do they change depending on regime? Because this is a quantile-based method, it is fair to include quantile scores as well (see Gneiting and Raftery 2007 for details).
\end{commentblock}

\responseheading
\begin{responsebox}
We agree. In the revised manuscript, forecast-window CRPS is now reported explicitly for the out-of-sample forecasting exercise, and we also add targeted quantile check-loss diagnostics. The CRPS comparison across cutoffs, benchmark models, and raw forecast products is reported in HE-2.

We use CRPS as the primary summary score because the object of interest is the full synthesized predictive distribution rather than any single quantile in isolation, and CRPS is an integrated quantile-score criterion. To complement that full-distribution summary, we report quantile check losses at the targeted levels \(\tau\in\{0.05,0.20,0.35,0.50,0.65,0.80,0.95\}\), using USGS observations as verification targets. We include these diagnostics for the four main synthesis competitors \texttt{exAL-M-T1}, \texttt{AL-M-T1}, \texttt{exAL-U-T1}, and \texttt{AL-U-T1}, so the reader can see how predictive performance changes across the forecast distribution and across cutoff windows.

\medskip
\noindent The table reports mean forecast-window quantile check loss at the targeted quantiles for the four principal synthesis competitors, on the same \(\log(1+Q)\) scale used in the CRPS calculations. Lower values indicate better quantile-level predictive performance, and within each cutoff panel the smallest value in each quantile column (ties included) is shown in bold.\par
\medskip

\begin{center}
\tiny
\setlength{\tabcolsep}{3pt}
\begin{tabular}{>{\ttfamily}l rrrrrrr}
\toprule
Model & q0.05 & q0.20 & q0.35 & q0.50 & q0.65 & q0.80 & q0.95 \\
\midrule
\multicolumn{8}{l}{\textit{Cutoff 01/23/2021}} \\
exAL-M-T1 & 0.0292 & 0.0791 & \textbf{0.0989} & \textbf{0.0997} & \textbf{0.0937} & 0.0752 & \textbf{0.0607} \\
AL-M-T1 & \textbf{0.0237} & \textbf{0.0763} & 0.1010 & 0.1002 & 0.0992 & \textbf{0.0732} & 0.0696 \\
exAL-U-T1 & 0.0306 & 0.1020 & 0.1546 & 0.1959 & 0.2144 & 0.1998 & 0.1169 \\
AL-U-T1 & 0.0297 & 0.1002 & 0.1521 & 0.1952 & 0.2293 & 0.2122 & 0.0830 \\
\addlinespace[1pt]
\multicolumn{8}{l}{\textit{Cutoff 11/12/2021}} \\
exAL-M-T1 & 0.0064 & \textbf{0.0167} & 0.0257 & \textbf{0.0149} & \textbf{0.0091} & \textbf{0.0136} & 0.0090 \\
AL-M-T1 & \textbf{0.0060} & 0.0222 & \textbf{0.0253} & 0.0159 & 0.0136 & 0.0210 & 0.0261 \\
exAL-U-T1 & 0.0159 & 0.0576 & 0.0876 & 0.1055 & 0.1034 & 0.0795 & \textbf{0.0043} \\
AL-U-T1 & 0.0153 & 0.0571 & 0.0864 & 0.1016 & 0.1000 & 0.0743 & 0.0072 \\
\addlinespace[1pt]
\multicolumn{8}{l}{\textit{Cutoff 12/21/2021}} \\
exAL-M-T1 & \textbf{0.0611} & \textbf{0.1486} & \textbf{0.1083} & \textbf{0.1160} & \textbf{0.1506} & \textbf{0.1479} & \textbf{0.0676} \\
AL-M-T1 & 0.0755 & 0.2203 & 0.1765 & 0.1190 & 0.2399 & 0.2274 & 0.1186 \\
exAL-U-T1 & 0.0885 & 0.3269 & 0.5360 & 0.7243 & 0.8671 & 0.9284 & 0.6705 \\
AL-U-T1 & 0.0893 & 0.3267 & 0.5342 & 0.7218 & 0.8544 & 0.8936 & 0.4532 \\
\addlinespace[1pt]
\multicolumn{8}{l}{\textit{Cutoff 05/11/2022}} \\
exAL-M-T1 & \textbf{0.0049} & 0.0126 & 0.0140 & 0.0131 & 0.0121 & \textbf{0.0098} & \textbf{0.0044} \\
AL-M-T1 & \textbf{0.0049} & \textbf{0.0111} & \textbf{0.0130} & \textbf{0.0127} & 0.0120 & 0.0100 & 0.0091 \\
exAL-U-T1 & 0.0117 & 0.0318 & 0.0368 & 0.0240 & 0.0117 & 0.0244 & 0.0201 \\
AL-U-T1 & 0.0116 & 0.0313 & 0.0356 & 0.0235 & \textbf{0.0114} & 0.0242 & 0.0227 \\
\addlinespace[1pt]
\multicolumn{8}{l}{\textit{Cutoff 12/25/2022}} \\
exAL-M-T1 & \textbf{0.0569} & \textbf{0.1758} & \textbf{0.1971} & \textbf{0.2308} & \textbf{0.2494} & \textbf{0.2376} & 0.1480 \\
AL-M-T1 & 0.1298 & 0.4368 & 0.5299 & \textbf{0.3773} & \textbf{0.2639} & 0.2556 & \textbf{0.0944} \\
exAL-U-T1 & 0.1403 & \textbf{0.3706} & 0.4925 & 0.6082 & 0.6743 & 0.6210 & 0.2494 \\
AL-U-T1 & 0.1440 & 0.3883 & 0.4996 & 0.6177 & 0.7366 & 0.7186 & 0.3549 \\
\bottomrule
\end{tabular}
\end{center}

The main practical pattern is that the multivariate synthesis models dominate the more difficult windows, with \texttt{exAL-M-T1} especially strong in the demanding 12/21/2021 and 12/25/2022 panels, while the univariate references win only isolated cells. Together with the CRPS comparison in HE-2, these quantile diagnostics show that the forecasting advantage of the multivariate synthesis models is visible both at the full-distribution level and across the targeted quantile levels. These results are now summarized in the revised forecasting-validation section of the manuscript.

\end{responsebox}


\commentheading{\HE{5}}
\begin{commentblock}
- It would be helpful for the reader to have access to the estimation and forecasting code for use in other basin applications.
\end{commentblock}

\responseheading
\begin{responsebox}
We agree. We now state explicitly in the revised manuscript that the reusable exDQLM estimation code is available through the CRAN R package \texttt{exdqlm}, and that the end-to-end forecasting workflow used in this study is available in the project repository at \url{https://github.com/AntonioAPDL/Project1}. Before resubmission, we will archive a permanent release of that repository and cite it explicitly in the manuscript. We also clarify that the reusable part is the model-fitting and forecasting workflow itself, whereas applying it to a new basin still requires constructing a basin-specific, version-consistent archive of observations, retrospective products, forecasts, and covariates.
\end{responsebox}


\commentheading{\HE{6}}
\begin{commentblock}
- Something that wasn't clear to me in the application was: is this in-sample, or out-of-sample validation? It appears that the model was fit to the data that is being used in validation, which isn't realistic. Please perform an appropriate cross-validation study to investigate the approach's actual ability to forecast unseen data.
\end{commentblock}

\responseheading
\begin{responsebox}
We agree that this needed to be clarified. The revised forecasting evaluation is out-of-sample and uses five rolling-origin cutoff-based forecasting folds.

For each cutoff date \(\textbf{c}\), the model is fit using only information available through \(\textbf{c}\): observed discharge up to \(\textbf{c}\), retrospective/historical products available at \(\textbf{c}\), and forecast products issued at or before \(\textbf{c}\). Post-cutoff USGS observations are used only for verification. By contrast, the post-cutoff forecast inputs that were already available at \(\textbf{c}\), including the forecast ensembles and the forecast precipitation and soil-moisture covariates used in the transfer component, are used to generate the forecast-window predictive distributions.

As noted in HE-2, the five cutoffs were retained only when the forecast inputs, retrospective products, and forecast covariates were all archive-feasible and version-consistent. The evaluation folds were therefore determined by timing and data availability, not by forecast performance.

\end{responsebox}


\commentheading{\HE{7}}
\begin{commentblock}
- The weighted combination of prior forecasts at differing horizons is curious to me. Presumably the most recent forecasts should be better with more available atmospheric data, whereas longer lead-time forecasts likely exhibit more bias. How does the model perform if you only use the most recent forecast (which I would expect to be the highest quality)?
\end{commentblock}

\responseheading
\begin{responsebox}
We agree that, from an operational forecasting perspective, the most recent forecast ensemble available at each cutoff is the natural reference. We therefore reran the forecasting analysis using only the latest available forecast ensemble, rather than combining earlier issuances. The substantive conclusions remained unchanged: the revised HE-2 comparison still shows \texttt{exAL-M-T1} as the best-performing model in all five cutoffs and better than \texttt{AL-M-T1} in all five. We therefore adopt the latest-forecast-only protocol throughout the revised forecasting analysis.
\end{responsebox}


\newpage
\section{Response to Reviewer 1}

%\commentheading{\RoneO}
\begin{commentblock}

Reviewer 1 Comments to the Author

This paper develops a Bayesian quantile regression approach, based on asymmetric Laplace distributions, to predict and forecast streamflow in the Santa Cruz region of the US. The work appears strong in the development of the Bayesian models and the novelty in the extension of inference methods is accepted. However, the improvement of forecasts through dynamical error correction is a common strategy and the novelty of this part may need to be elucidated further. The paper is framed as a forecasting paper, however the forecasting component is limited and robust forecast evaluation is absent. I recommend that some substantial revisions, mainly structural, are required before proceeding with publication. My comments below don’t cover everything, but are intended as a push into reshaping:
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that, in its original form, the manuscript gave too much emphasis to model development and not enough to forecast validation. The revised manuscript addresses that directly by centering the forecasting analysis on multiple rolling-origin cutoffs over a 29-day horizon, comparing the proposed method against simpler Bayesian alternatives and the raw ECMWF/GloFAS and NWS forecast products, reporting both CRPS and targeted quantile diagnostics, and using only the most recent forecast ensemble available at each cutoff.

We also revised how the contribution is stated. In the revised manuscript, the main contribution will be presented as the Bayesian quantile-based correction-and-synthesis framework together with its forecasting performance in this application, rather than dynamical error correction in the abstract. The remaining issues concerning motivation, model-to-results linkage, and presentation are addressed point by point below.
\end{responsebox}

\begin{commentblock}
Major comments:
\end{commentblock}

\commentheading{\RoneM{1}}
\begin{commentblock}
1. In the introduction and elsewhere, the “cascade of uncertainty” is not distinguished between meteorological uncertainty and hydrological uncertainty. This is not necessarily a major problem with a Bayesian model that combines sources of uncertainty, but I find the introduction and motivation less compelling when hydrological and meteorological concepts are mixed. For example, the paragraph that starts off “Hydrological predictions are often produced using physical models…” diverts to discussions of under-dispersion in ensembles and perturbation methods in weather forecasts. I would suggest restructuring the introduction to cover different sources of uncertainty before explaining how uncertainty can be consolidated in a Bayesian framework.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the introduction does not currently distinguish meteorological and hydrological uncertainty clearly enough, and that this weakens the motivation. In the revised manuscript, we will reorganize the introduction so that these uncertainty sources are separated before the Bayesian framework is introduced, and we will shorten the discussion of atmospheric ensemble-generation methods so that the focus stays on the sources of uncertainty most directly relevant to the correction-and-synthesis problem studied here.
\end{responsebox}

\commentheading{\RoneM{2}}
\begin{commentblock}
2. The links between the model formulation and the results are not clear to me. For example, three models (A, B and C) are developed in section 2. It would be helpful to explicitly link the models to the results being discussed in section 3.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the current A/B/C presentation does not make the connection between the model formulation and the reported results clear enough. In the revised manuscript, we will present the final forecasting specification more directly and use the staged development only as supporting exposition, rather than as the main organizing device for the results. We will also revise the opening of the results section so that the reader can see immediately which specification is being evaluated and how the reported comparisons relate to the final forecasting framework.
\end{responsebox}

\commentheading{\RoneM{3}}
\begin{commentblock}
3. The paper is maths heavy, so it may be beneficial to reduce the equations and mathematical details. The amount of detail given may be highly suitable for a dissertation, but some details are not necessary for a paper. For example, in section 2.7, PITs are described in detail, however, it is followed that CRPS is chosen for model selection instead and PITs are not used. Suggest removing PITs in this case. As another example, no quantile crossing is observed, however a two-step method is presented to “resolve” quantile crossing. I suggest reconsidering how much detail is needed for the Posterior Predictive Synthesis part.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the manuscript currently contains more mathematical detail than is needed for a journal article, and we will simplify the presentation substantially. In particular, we will remove the detailed PIT development from the main text, since PITs are not used in the final reported evaluation and CRPS is the main criterion used for model comparison and forecast assessment.

More broadly, we will reduce intermediate derivational detail and keep the focus on the forecasting quantities that are actually used in the revised results section. For posterior predictive synthesis, we will retain only a concise description in the main text, because that step is part of the contribution of the paper; the quantile-crossing safeguard will be mentioned briefly as a robustness device rather than developed at length.
\end{responsebox}

\commentheading{\RoneM{4}}
\begin{commentblock}
4. If I have not misunderstood, only one short forecast has been evaluated for a moderate flood from 2022-12-25 to 2023-01-22. Is it possible to provide more evidence for the use of the model for forecasting high, low and moderate events? Or the continuous period 2023 to present? Going to the previous comment, PITs and CRPS have been used for model selection (section 2.7) rather than forecast verification. I would suggest that in an expanded evaluation of forecast performance that CRPS and PITs would be useful tools.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the original manuscript placed too much weight on the 2022-12-25 to 2023-01-22 forecast window. In the revised manuscript, the forecasting evaluation is expanded to five rolling-origin out-of-sample cutoffs spanning different hydrological settings, within the range allowed by archive-feasible and version-consistent historical forecast inputs, so the evidence is no longer tied to a single moderate-flood episode. Forecast performance is now assessed directly on those forecast windows using CRPS together with targeted quantile diagnostics. The single 2022-12-25 synthesis figure is retained only as a representative illustration of the selected model at one forecast origin, while the historical regime figures and long-cycle appendix figure are treated as descriptive historical summaries rather than as additional forecast-validation evidence. Consistent with the streamlining described in Response R1-M3, we do not retain a separate PIT analysis in the main text because PIT is not part of the final revised comparison.
\end{responsebox}

\commentheading{\RoneM{5}}
\begin{commentblock}
5. A robust discussion of how the method can be set up for fair forecast assessment using cross-validation might be required.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that fair assessment of this method must be organized around forecast origins rather than a conventional single split of the time series. The revised analysis already does this through five rolling-origin cutoff-based folds, which are the appropriate analogue of cross-validation in this setting. The same design could be extended to broader tuning or validation over a larger set of feasible cutoffs, but in practice those cutoffs are constrained by archive/version consistency and should not be taken so densely that heavily overlapping forecast windows overrepresent the same hydrological regime. The revised manuscript now makes this evaluation setup explicit.
\end{responsebox}

\subsection{Reviewer 1 --- Minor comments }
\begin{commentblock}
Minor comments:
\end{commentblock}

\commentheading{\Ronem{1}}
\begin{commentblock}
1. Introduction: While it is true that “Hydrological predictions are often produced using physical models”, it could be worthwhile noting that conceptual models are often more practical for prediction.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree. The current sentence is too narrow. In the revised manuscript, we will broaden it to note that operational hydrological forecasting uses conceptual as well as physically based models, and that conceptual models are often more practical for prediction because they are typically simpler to specify, calibrate, and use in forecasting applications.
\end{responsebox}

\commentheading{\Ronem{2}}
\begin{commentblock}
2. Section 2.1: I’m not familiar with the term “flexile quantile estimation”. Would it be better to say “flexible quantile estimation”?
\end{commentblock}
\responseheading
\begin{responsebox}
We agree. This appears to have been a typo on our side rather than intended terminology, and we will correct it in the revised manuscript.
\end{responsebox}

\commentheading{\Ronem{3}}
\begin{commentblock}
3. Section 2.3: Agree reanalyses have fewer problems that forecasts in terms of data gaps and uncertainties; however, it is important to note that fields like rainfall in ERA5 are filled out with short-run forecasts and are not completely deterministic.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the current wording in Section 2.3 is too strong. Our intent was only to distinguish single-valued retrospective products from probabilistic forecast products, not to suggest that the former are uncertainty-free or equivalent to observations. In the revised manuscript, we will replace the deterministic language with more precise wording and note explicitly that products such as ERA5 can include short forecast components, so these inputs should be understood as retrospective or reanalysis-based products with their own uncertainties.
\end{responsebox}

\commentheading{\Ronem{4}}
\begin{commentblock}
4. Section 2.3: Introduce the USGS measurements and difference with reanalysis products. It may be useful to have a separate data and methodology section.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the USGS observations and their role relative to the retrospective products are introduced too indirectly. In the revised manuscript, we will state earlier and more explicitly that the USGS series is the observed target, whereas the retrospective products are external historical inputs, and we will reorganize the application material so that observations, retrospective products, forecast products, and forecast covariates are introduced in a clearer order.
\end{responsebox}

\commentheading{\Ronem{5}}
\begin{commentblock}
5. How is non-zero precipitation handled, is it through data censoring?
\end{commentblock}
\responseheading
\begin{responsebox}
This was not described clearly enough in the manuscript. In the current specification, precipitation is not handled through a separate censoring, zero-inflation, or occurrence/intensity model. Instead, it enters as an external covariate in the transfer function, so zero-precipitation days are retained as zero and its intermittent behavior is handled through the supplied covariate path and transfer dynamics rather than through a separate precipitation model. We will make this explicit in the revised manuscript.
\end{responsebox}

\commentheading{\Ronem{6}}
\begin{commentblock}
6. Section 3: lagged forecasts are weighted into an ensemble forecast for the target time rather than using the latest available forecast. In my experience, this can have the effect of degrading skill. Did the authors find this was beneficial?
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that this concern is well taken from an operational forecasting perspective. In the revised analysis, we no longer combine older forecast issuances for the target time; at each cutoff we use only the most recent forecast ensemble available. The revised forecasting results reported in this response letter and referred to in the manuscript now follow that latest-forecast-only protocol.
\end{responsebox}

\commentheading{\Ronem{7}}
\begin{commentblock}
7. Section 3.2: The title here is somewhat vague “General results”. Given Section 3 is supposed to be on forecasting and these results appear to be about in-sample prediction, I suggest reorganising the headings and separating out model checking from forecasting.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the current organization of Section 3 is not clear enough. In the revised manuscript, we will replace vague headings such as ``General Results'' and reorganize the material so that application setup, historical fit and parameter interpretation, and out-of-sample forecasting results are presented in separate subsections. This will separate setup, historical behavior, and forecasting evidence more clearly.
\end{responsebox}

\commentheading{\Ronem{8}}
\begin{commentblock}
8. Table 1 and 2: Check captions, should it be posterior mean or median?
\end{commentblock}
\responseheading
\begin{responsebox}
We agree. The original labeling of Tables 1 and 2 was inconsistent: the entries reported there are posterior medians with 95\% credible intervals, not posterior means. In the revised manuscript, the captions, table notes, and surrounding text now use that terminology consistently.
\end{responsebox}

\commentheading{\Ronem{9}}
\begin{commentblock}
9. Figures 8 and 9: Suggest some explanation around the approx. constant variance in Figure 8 and variable predictive distributions in Figure 9.
\end{commentblock}
\responseheading
\begin{responsebox}
We agree that the discussion of these figures was not clear enough. In the revised manuscript, the main forecasting evidence comes from the expanded multi-cutoff comparisons rather than from the illustrative figures alone. The retained synthesis figure is now described explicitly as a representative single-cutoff illustration of the selected model, while the historical-only counterfactual is kept only as an appendix reference with a different role. The historical regime figures and the long-cycle seasonal figure are likewise described as historical summaries of the fitted specification rather than as like-for-like forecast-validation comparisons.
\end{responsebox}

\end{document}
